\documentclass[12pt]{article}
\usepackage{amsmath,amssymb, amsfonts, amsthm,amscd}
\usepackage[T2A]{fontenc}
\usepackage[cp1251]{inputenc}
\usepackage[russian,ukrainian,english]{babel}
\usepackage{graphicx}

\pagestyle{empty}

\textheight=235mm \textwidth=155mm \voffset=-8mm \hoffset=-14mm
\sloppy

\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem*{proposition*}{Proposition}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{corollary*}{Corollary}

\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newtheorem*{definition*}{Definition}
\newtheorem*{remark*}{Remark}
\newtheorem*{example*}{Example}

\newcommand{\address}[2]
{\vspace{-3mm}\medskip \noindent
\begin{minipage}[t]{7.5cm}
\small{#1 \\
\tt{#2}}
\end{minipage}}

\renewcommand\refname{\large \textbf{References}}

\begin{document}
\begin{center}
{\LARGE Differentiable finite-state izometries and izometric
polynomials of  the ring of integer 2-adic numbers.}
\end{center}
\vskip 0.1cm \centerline{\large \large Denis Morozov } \vskip
0.5cm

The aim of the report is to construct requirements which describe
izometric polynomials of the ring of integer 2-adic numbers.

The results of this report continue investigations of 2-adic group
automatous with the 2-adic izometric functions technique.
Polynomials build the important class of izometric function that
is why we investigate them.

In addition we investigate differentiable finite-state izometries.
The class of finite-state izometries is very important class of
izometries and is the object of investigation in many scientific
researches.

\begin{definition}
Define $S_n(x_1,x_2)$ as  $$S_n(x_1,x_2)=\sum_{k=0}^{n-1}
x_1^{n-k-1}\cdot x_2^k $$
 \end{definition}


 \begin{example} $S_1(x_1,x_2)=1$, $S_2(x_1,x_2)=x_1+x_2$, $S_3(x_1,x_2)
 =x_1^2+x_1\cdot x_2+x_2^2\ $ etc.
 \end{example}
 \begin{definition}  Define function $\mu(x)=\overline{ x}$:

$$
\mu(x)=\begin{cases}
0, x\in 2Z_2\\

1,x\in Z_2^*
\end{cases}
$$
 \end{definition}





 \begin{definition}
 $$D_f(x_1,x_2)=\frac{f(x_1)-f(x_2)}{x_1-x_2}$$
 \end{definition}


 \begin{lemma}\label{izomumov1}
 Polynomial $f(x)\in Z_2[x]$ is isometry, if and only if $$\forall\ x_1,x_2 \in Z_2\  \overline{D_f}(x_1,x_2)=1$$
 \end{lemma}

 \begin{definition}
 Let's define for the polynomial $f(x)=a_0+a_1x+a_2x^2+...+a_nx^n$ values $A_f$ and $B_f$:
 $$ A_f=\mu \left(\sum_{k=1}^{[\frac{n+1}{2}]}a_{2k}\right), B_f=\mu \left(\sum_{k=2}^{[\frac{n+1}{2}]}a_{2k-1}\right)$$
  \end{definition}


  \begin{theorem}\label{istformul}
    $\overline{ a}_1\oplus (A_f\cap (\overline{x}_1\oplus \overline{x}_2))\oplus (B_f\cap (\overline{x}_1\cup \overline{x}_2))$
    is true if and only if $\overline{ a}_1=1,\ A_f=0,\ B_f=0$
  \end{theorem}

  \begin{theorem}\label{naslidok2} According to theorem \ref{istformul}, polynom
   $f(x)=a_0+a_1x+a_2x^2+...+a_nx^n$ is isometry if and only if when $a_1$
   is invertible ( odd ) integer 2-adic number,
   the sum of coefficients with even numbers greater then 0 is even 2-adic number
    and the sum of coefficients with odd numbers greater then 1 is
    even
    2-adic number.
   \end{theorem}

   \begin{theorem} Finite-state izometry of the ring $Z_2$ is
   differentiable if and only if it's parted linear.
   \end{theorem}






\vspace{-5mm}\small
\begin{thebibliography}{3}
\bibitem{ item1 }Morozov Denis,      Linear automatous which are finite-state
conjugated.  //  Conf. "Groups generated by automata" in
Switzerlend:  Abstr.  Ascona,  February,  2008

\bibitem{ item2}Morozov Denis,      Linear function which are conjugated in
the group  $FAutT_2$  of  finite state automatous.
// 6th Int.  Algebraic Conf.  in  Ukraine:  Abstr.
Kamyanets-Podilsky, July  1-7,  2007.  D. 140.

\bibitem{ item3}Morozov Denis,  The structure of centralizers of maximal
pro-oder elements in the group  $AutT_2$ . // 5th Int. Algebraic
Conf. in Ukraine: Abstr. Odessa, July 20-27, 2005.  P. 37.

\end{thebibliography}

\address{Kharkiv road, 17/r.203, Kiev}{denis.morozov178@gmail.com}
\end{document}
